### 2014-01-26 proposal/proposal.tex
Added Experiment section

>>>>

\section*{Experiment}
Unfortunately, we do not have user data on which to test our methods, since the system
has never been used before. Instead, we will simulate user behavior to get a rough
estimate of performance. To do this, we make the following assumptions:

\begin{enumerate}
\item There are a number of universal hidden features that describe each product.
These features could be something as tangible as color or as intangible as
`hipness'. Note that like latent topics, these features need not be
representable by an explicit, expressible concept.

\item Each user has a preference for products based on these hidden features. For
instance, a user could care a lot that a product is `hip', not care
at all what color it is, and have a mild preference for slim-fitting products,
assuming these are all hidden features of products.
\end{enumerate}

For testing, we simplify the model by assuming that there is only one hidden
feature. We model this as color. Since the learning algorithm is blind to color
data, this should be as difficult to determine as a less tangible feature, such
as style, but color is easier for us to use, since it is metadata that we
have about each product. Next, we create a number of fake users, defined by their color
preferences. These preferences are modeled as multinomial distributions. For instance, if
there are only the three colors red, white, and blue, a user could care deeply
that their product is red by having a (1, 0, 0) distribution over those colors.
Or, if the user doesn't care what color their product is, their distribution
would be (0.33, 0.33, 0.33).

We can then construct a number of users with different distributions, using an
arbitrary Dirichlet distribution or our creation. This way, we can model the
phenomenon that preferences are not uniform; many users have the same style
preferences as each other and some styles are less popular than others.

With this model, we can construct a number of fake users with different
preference distributions. Based on these distributions, we can
probabilistically choose which items each user likes and then simulate their
interaction with the system. Then we can train the system on a number of fake
users to learn from their behavior. For testing, we then introduce new fake users,
and measure how well the system can predict the underlying color dtistributions of
the users. We will aim to increase the accuracy of the predicted distributions and
reduce the number of shown products needed to learn it.
